Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-10 paper.tex
Work on Against and Christian Response sections.
Still need to add more to the Christian response (and include it more
throughout the essay). I also still need to add more to the Against
section, not just the malware section.

\begin{displayquote}
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  Thomas Jefferson~\cite{barlow:wine}
\end{displayquote}
It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched.

@@

Having a very firm grip on what citizens can see on the internet is one of the key
characteristics of a despotic government. Such governments know that if they can control
the flow of information on the Internet, it becomes much easier to keep the populace under
control. The government's imposing of restrictions on the Internet is clearly seen when
\textcquote{current:jigsaw} {Tunisia significantly ramped up its already aggressive
blocking of specific websites in response to unrest that would ultimately unseat its
government.} Even more extreme is when governments shutdown the internet entirely to
quickly cease the spread of information. This is exactly what happened on January 28, 2011
in Egypt: \textcquote{current:jigsaw} {Almost simultaneously, about 3,500 individual
Border Gateway Protocol routes [...] were withdrawn on orders from the Egyptian
government, cutting the country off from the rest of the world and bringing internal
communication to a halt.} Fortunately, as already mentioned earlier, piracy excels at
spreading information even when there are those that do not want it spread. BitTorrent is
a peer-to-peer file sharing protocol that is often used when pirating content on the
Internet. A peer-to-peer protocol, by its very nature, does not require a centralized
server to store all the files that are to be shared. Instead, the source of the file is
each person who has the file downloaded. What this means for those under the rule of an
oppressive government is that they can spread information to others in such a way that the
government cannot easily block its source. Pieces of the information are sent to the one
downloading the file from everyone who had the file. There is no single source of the
information that the government can block to stop the spread. By a similar token, there
are peer-to-peer instant messaging applications that do not require an internet connection
to function; you need only be in the vicinity of other people that the message can hop
through to get to the destination. Both of these tools, in the context of piracy, facilitate
the illegal spread of information, but in the context of a despotic government, can be
employed to subvert their attempts at quelling the dispersal of information that could be
harmful to their rule.

@@

\subsubsection{Malware}
Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed. Piracy
circumvents mainline distribution channels that may incorporate secure policies
of data integrity, authenticity, and privacy. Some piracy tools provide
some ways to vet the authenticity of an uploader based on past uploads or based
on the user's relationship with the piracy/torrenting
site\footnote{%
  \href{https://pirates-forum.org/Thread-ThePirateBay-Want-Trusted-VIP-Status-Pink-Green-Skull-See-Here}{ThePirateBay},
  for example provides icons to display whether a user is \emph{Trusted},
  \emph{VIP}, or \emph{Moderator}%
}, but not all sites provide these metrics or warnings for the average end-user.
Instead, the burden is often on the end-user, and it is not unfair to assume
that the average person would not be able to analyze downloaded software for
malware.

% TODO: Add an example of malware distributed via piracy

@@

\textcquote{mrad:effects-of-ip}[.]{%
  According to Gould and Gruben (1996), IPRs protection stimulates economic
  growth if it is accompanied by a policy of trade liberalization. By
  encouraging initiatives to innovate, IPRs protection may influence the
  economic growth of an open country. Park and Ginarte (1997) found that IPRs
  protection affects economic growth indirectly by stimulating the accumulation
  of factors of production such as physical capital and R\&D capital%
}
Piracy, therefore, discourages innovation in the capitalist marketplace.

% TODO
\section{Christian Response}
A Christian response to piracy should honestly take into account both sides of
the debate. As shown above, piracy does have some merit to it. Christians have
to admit that piracy-promoting tools do enable

% 1 Peter 2:13-17
% Romans 13:4-5

\begin{enumerate}
  \item Drawing distinctions: Paywall to information is different from
    withholding information for sake of security

  \item Paywalls provide the means of living for artists, writers, \&c. Providing
    ways to circumvent these when unnecessary may hinder their livelihoods.

  \item Betterment of mankind as a whole, should not be behind a paywall

  \item Piracy provides an avenue for missionary outreach; piracy provides
    means of secret dissemination within an oppressive regime.

  \item Piracy provides the means for access to content/information without
    much accountability
\end{enumerate}

>>>>

\blockcquote{barlow:wine}{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  \emph{Thomas Jefferson}%
}

It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched.

@@

Having a very firm grip on what citizens can see on the internet is one of the key
characteristics of a despotic government. Such governments know that if they can control
the flow of information on the Internet, it becomes much easier to keep the populace under
control. The government's imposing of restrictions on the Internet is clearly seen when
\textcquote{current:jigsaw} {Tunisia significantly ramped up its already aggressive
blocking of specific websites in response to unrest that would ultimately unseat its
government.} Even more extreme is when governments shutdown the internet entirely to
quickly cease the spread of information. This is exactly what happened on January 28, 2011
in Egypt: \textcquote{current:jigsaw} {Almost simultaneously, about 3,500 individual
Border Gateway Protocol routes \textelp{} were withdrawn on orders from the Egyptian
government, cutting the country off from the rest of the world and bringing internal
communication to a halt.} Fortunately, as already mentioned earlier, piracy excels at
spreading information even when there are those that do not want it spread. BitTorrent is
a peer-to-peer file sharing protocol that is often used when pirating content on the
Internet. A peer-to-peer protocol, by its very nature, does not require a centralized
server to store all the files that are to be shared. Instead, the source of the file is
each person who has the file downloaded. What this means for those under the rule of an
oppressive government is that they can spread information to others in such a way that the
government cannot easily block its source. Pieces of the information are sent to the one
downloading the file from everyone who had the file. There is no single source of the
information that the government can block to stop the spread. By a similar token, there
are peer-to-peer instant messaging applications that do not require an internet connection
to function; you need only be in the vicinity of other people that the message can hop
through to get to the destination. Both of these tools, in the context of piracy, facilitate
the illegal spread of information, but in the context of a despotic government, can be
employed to subvert their attempts at quelling the dispersal of information that could be
harmful to their rule.

@@

\subsubsection{Malware}
The intersection of trust and computing is not a new topic. Ken Thompson, the
creator of the Unix operating system, made this the topic of his Turing Award
lecture. In his lecture, he poses the question,
\textcquote[761]{thompson:trust}[.]{%
  to what extent should one trust a statement that
  a program is free of Trojan Horses? Perhaps it is more important to trust the
  people who wrote the software%
} With piracy, however, we add an additional actor in this chain of trust.
Thompson's lecture focuses solely on the developer-to-user relationship of
trust, with the assumption of an open-source project. Thompson, thus, comments
on how \textcquote[763]{thompson:trust}{%
  \textins{s}uch blatant code would not go undetected for long. Even the most
  casual perusal of the source of the C compiler would raise suspicions%
} When piracy is the method of distribution, however, the assumption of
equality between the source code and the delivered software does not hold. The
pirated software may have been tampered with, and the user has no simple way to
detect changes in the file(s) without doing some (often) complicated forensic
work. Although anti-malware tools may mitigate these issues, the problem of
trust still holds, and the anti-malware tools are not perfect. The character of
the seeder must be questioned, and it already stands on shaky ground if the
legality of their actions speaks for their moral compass and trustworthiness.

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed. Piracy
circumvents mainline distribution channels that may incorporate secure policies
of data integrity, authenticity, and privacy. There are piracy tools and sites
that provide some ways to vet the authenticity of a user based on the user's
previous history and relationship with the piracy community. For example,
ThePirateBay, one of the most popular pirating sites, displays the status or
class of their users and holds these users to higher standards in order to
retain trust with the site's end users.~\cite{suprbay:status} Nevertheless, not
all sites provide these metrics or warnings for the average end-user. Instead,
the burden is often on the end-user, and it is not unfair to assume that the
average person would not be able to analyze downloaded software for malware.

The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by Mezzour et al. reveals that piracy is not equal
around the globe, and it poses serious problems especially for people in
poor countries where piracy is widespread. Although they hypothesized, like
other researchers, that \textcquote{mezzour:empirical-study}[,]{%
  cyber criminals would target rich countries because the monetary benefit of
  compromising rich people's computers is higher
} but they found that, \textcquote{mezzour:empirical-study}[.]{%
  surprisingly, poor countries in Sub-Saharan Africa because of the low cost of
  attacking computers in this region%
} Mezzour et al. conclude that, due to the high correlation between piracy
and malware, one of the policy implications is that Sub-Saharan Africa requires
reducing piracy to combat the spread of malware.

% TODO: Add an example of malware distributed via piracy, see pcmag source

@@

\blockcquote{mrad:effects-of-ip}[.]{%
  According to Gould and Gruben (1996), IPRs protection stimulates economic
  growth if it is accompanied by a policy of trade liberalization. By
  encouraging initiatives to innovate, IPRs protection may influence the
  economic growth of an open country. Park and Ginarte (1997) found that IPRs
  protection affects economic growth indirectly by stimulating the accumulation
  of factors of production such as physical capital and R\&D capital%
}
Piracy, therefore, discourages innovation in the capitalist marketplace.

% TODO
\section{Christian Response}
A Christian response to piracy should honestly take into account both sides of
the debate. As shown above, piracy does have some merit to it. Christians have
to admit that piracy-promoting tools do enable equal access for those in need,
but, at the same time, we must recognize that the human nature is not perfect,
but is full of evil thoughts (Matthew 15:19). Our human corruption manifests
itself in many ways through our lives and actions, but, as explored in this
paper, it also presents itself in the software we share. Our deceitful hearts
(Jeremiah 17:9) make it hard to trust the software we download, but reckless
use of piracy ignores advice and is therefore the way of the fool where people
fall (Proverbs 12:15, 11:14).

On the one hand, a Christian use of piracy should be respectful of authority.
We are called to do this regardless of punishment, but as a matter of
conscience (Romans 13:4--5). We are to exercise our freedom respectfully and
not as a cover-up for evil (1 Peter 2:13--7). In other words, we should consider
both the consequences we may incur and the image we portray carefully before
making a conclusion about the practice of piracy. A proper consideration of
privacy should not ignore the serious ramifications and associations that come
with it.

On the other hand, piracy, when used properly, is able to be used for good
causes that serve God rather than men (Acts 5:29). Academic articles,
especially from medical journals, are crucial for the development of humanity
and the saving of lives. In these cases, when capitalist motivators impede these
greater goods, one should not turn a blind eye, but instead we should remember
the poor and those in need (Proverbs 19:17, 22:9, 15:11; Galatians 2:10). Cases
like these present valid concerns in which piracy appears to provide a viable
solution to the problems brought about by human greed.
